---
title: "ENVS 193DS Week 7"
author: "Lena Hicks"
date: "5/17/2023"
output: html_document
execute:
  warning: false
  message: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r libraries}
library(tidyverse)
library(here)
library(lterdatasampler)

library(performance)
library(broom)
library(ggeffects)
library(ggmice)
library(janitor)
```

# Linear Models

How does stem length _predict_ stem dry mass?

```{r filtering-data}
maples_data <- hbr_maples %>% 
  clean_names() %>% 
  filter( year == 2003 & watershed == "Reference")
  
```

Visualizing missing data:

```{r missing-data-vis}
```

Create an exploratory data visulaization:

```{r data-vis}
ggplot(data = maples_data, aes(x = stem_length, y = stem_dry_mass))+
  geom_point()
```


let's try a model:

```{r linear-model-maples}
maples_model <- lm(stem_dry_mass ~ stem_length, data = maples_data)

maples_model
```

Check assumptions

1. linear relationship between variables: yes! (used the exploratory visulaization to check that)
2. independence of errors: yes! (making that assumption based on how data was collected)
3. homeskedasticiity of errors: yes! (making that descion from residual vs fitted plot/scale-location plots)
4. normally distributed errors: yes! (looking at QQ plot of residuals)

To get plots for last two assumptions, put plot(data set) in console and hit return for each plot

```{r checking-assumptions}
#allows us to plot same plots in one same grid
par(mfrow = c(2, 2))
plot(maples_model)
```


turn off the 2x2 grid

```{r turning-off-the-grid, results = FALSE}
dev.off()
```





